---
title: "About the data"
description: |
#author:
#  - name: Nora Jones 
#    url: https://example.com/norajones
#   affiliation: Spacely Sprockets
#   affiliation_url: https://example.com/spacelysprokets
#   date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Variables 
  - The data is extracted from from ICAO (International Civil Aviation Organization) API, occurred in the last 15 years (from Jan 2008 to May 2022).
  - Original ICAO API datasets link is available below. API key required, with 100 free calls available using a company email for subscription. Every accidents year dataset requires one different call (available in CSV or JSON format).
  https://applications.icao.int/dataservices/default.aspx
  
Columns:

- Date: Date of occurrence in datetime format (time is default 00:00:00.000Z)
- StateOfOccurrence: Country of occurrence
- Location: City or nearest city of occurrence
- Model: Aircraft type
- Registration: Aircraft registration code
- Operator: Name of Operator (airline, institution or responsible for the aircraft operation)
- StateOfOperator: Operator's country
- StateOfRegistry: Country of aircraft registration
- FlightPhase: Flight Phase of occurrence (take off, landing, approach, etc.)
- Class: Accident (unique value). rmk: only 'Accident' class was selected in this dataset (no incidens)
- Fatalities: Number of fatal victims
- Over2250: If aircraft basic operational weight (empty) is greater than 2250KG
- Over5700: If aircraft basic operational weight (empty) is greater than 5700KG
- ScheduledCommercial: If it was a scheduled commercial flight (airlines mostly)
- InjuryLevel: Level of injuries on person/people involved in the occurrence
- TypeDesignator: Aircraft type code (https://cfapps.icao.int/doc8643/reports/Part2-By%20Type%20Designator(Decode).pdf)
- Helicopter: if it was a helicopter
- Airplane: If it was an airplane
- Engine: Number of engines in the aircraft
- EngineType: Aircraft engine type (jet, turboprop or piston)
- Official: If ICAO was designated to participate in the accident investigation
- OccCats: All risk types involved in the occurrence, coded according to HRCs ( High Risks Categories codes) - ICAO
- Risk: Main risk type involved in the occurrence, coded according to HRCs(( High Risks Categories codes) - ICAO
- Year: Year of occurrence

## Data Preparation
Here are the packages I used for this data visualization:

```{r dataprep, echo= TRUE, eval=TRUE}
library(haven)
library(tidyverse)
library(modelsummary)
```

Read the data and clean it ready to use:
```{r importdata, echo=TRUE, eval=TRUE}
df<-read.csv("data/ICAO_accidents.csv") 
df %<% select(Date)

```








