---
title: "Number of Accidents Each Year and Risk Factors"
description: |
 The data visualization represent the number of accidents from 2008 to 2022 and represents the risk factor of the accidents. 

output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r importdata}
library(tidyverse)
library(ggthemes)
library(plotly)

df<-read.csv("data/ICAO_accidents.csv") 

#Country abbreviation to country full name
world <- read.csv("data/world.csv") %>% 
    rename(StateOfOccurrence = Abbreviation)

df <- left_join(df, world)
com <- filter(df, df$ScheduledCommercial == "True") %>% select(Year, Country, Model, Fatalities, Over2250, Over5700, InjuryLevel, Risk, FlightPhase, EngineType)


```

```{r echo=TRUE, eval=TRUE}
Ri_acc <- data.frame(table(com$Risk, com$Year)) %>% rename(Risk = Var1, Year = Var2)
sum <- aggregate(Freq ~ Risk, data = Ri_acc, FUN = "sum")
#Filter out if average each year less than 1 event 
filtered <- sum[sum$Freq >= 15, ]

Ri_acc <- Ri_acc[(Ri_acc$Risk %in% c("CABIN", "CFIT", "F-NI","LOC-I","RS","SCF","TURB")), ]

Ri_acc$Risk <- ifelse(Ri_acc$Risk == "SCF", "System/Component Failture or Malfunction",
                     ifelse(Ri_acc$Risk == "ARC", "Abnormal Runway Contact",
                           ifelse(Ri_acc$Risk == "CABIN", "Cabin Safety Events",
                                  ifelse(Ri_acc$Risk == "CFIT", "Controlled Flight Into or Toward Terrain",
                                         ifelse(Ri_acc$Risk == "F-NI", "Fire/Smoke",
                                                ifelse(Ri_acc$Risk == "LOC-I", "Loss of Control- In Flight",
                                                       ifelse(Ri_acc$Risk == "RS", "Runway Safety",
                                                              ifelse(Ri_acc$Risk == "TURB", "Turbulence Encounter",
                                         Ri_acc$Risk))))))))

```

```{r eval = TRUE, echo = TRUE}
fig <- plot_ly(data =Ri_acc, x = ~Year, y = ~Freq, color = ~Risk, size = ~Freq, type = "bar") %>%  
  layout(legend = list(y = -0.5, 
                       x = -0.1, 
                       orientation = "h")) %>%
  layout(title = "Risk Factors and Frequency Across 2008-2022")


fig
```

Please see the abbreviation in the [Risk Factor Hand Book](https://www.icao.int/APAC/Meetings/2012_APRAST/OccurrenceCategoryDefinitions.pdf)

This plot represents the number of accidents (from 2008 - 2022) each year and the risk factor of the accidents based on the result of aviation occurrence investigation.The x axis represents the year from 2008 to 2022, and the y axis represents the number of accidents. The risk factors are represented by the colors on the histogram. In the interactive graph, readers can click on to see the actual accidents number for the year. From this plot, we can easily distinguish that most of accidents occurred because of "Runway Safety", and there are most accidents happened in 2014. 

This plot is intended for a general audience. See the plots on the below for different iterations of this visualization.






