---
title: "Number of Fatality"
description: |
  A new article created using the Distill format.
author:
  - name: Nora Jones 
    url: https://example.com/norajones
    affiliation: Spacely Sprockets
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r importdata}
library(tidyverse)
library(ggthemes)
library(plotly)

df<-read.csv("data/ICAO_accidents.csv") 

#Country abbreviation to country full name
world <- read.csv("data/world.csv") %>% 
    rename(StateOfOccurrence = Abbreviation)

df <- left_join(df, world)
com <- filter(df, df$ScheduledCommercial == "True") %>% select(Year, Country, Model, Fatalities, Over2250, Over5700, InjuryLevel, Risk, FlightPhase, EngineType)


```

```{r echo=TRUE, eval=TRUE}
Ri_acc <- data.frame(table(com$Risk, com$Year)) %>% rename(Risk = Var1, Year = Var2)
```

```{r eval = T, echo = T}
plot_ly(data =Ri_acc, x = ~Year, y = ~Freq, color = ~Risk, size = ~Freq) 

```

[Risk Factor Hand Book](ttps://www.icao.int/APAC/Meetings/2012_APRAST/OccurrenceCategoryDefinitions.pdf)

This plot represents the number of accidents (from 2008 - 2022) each year and the risk factor of the accidents based on the result of aviation occurrence investigation.The x axis represents the year from 2008 to 2022, and the y axis represents the number of accidents. The risk factors are represented by the colors on the histogram. (I am going to make a change for the graph) In the interactive graph, readers can click on to see the actual accidents number for the year. From this plot, we can easily distinguish that most of accidents occurred because of "Runway Safety", and there are most accidents happened in 2004. 

This plot is intended for a general audience. See the plots on the below for different iterations of this visualization.






